A finite-state morphological transducer for Kyrgyz

### 2012-03-14 paper/paper.tex
various fixes
footnote 12

%FIXME: this should be closer to the 200 word limit, and less like the intro pargraph

@@

\subsection{Desonorisation}
Desonorisation \citep{washington10} happens to /N/ when it follows any consonant, and to /L/ when it follows a consonant of equal or lower sonority (i.e., /л/, nasals (/м/, /н/, /ң/), and obstruents, but not /й/, /р/, or vowels).  The resulting surface consonant is [д] for both /N/ and /L/, unless it follows a voiceless consonant, in which case it surfaces as [т].  An example includes the accusative and plural suffixes: % FIXME: This should point to the table ?

@@

%FIXME: do something with these: make them prettier, remove them, explain them better, ....?
\begin{figure}
\caption{Example of use of epenthetic vowel \{y\}.}
~\\

 орун:ор{\tt {\small \%\{y\%\}}}н~~ N-INFL~~ ;~~ ! ``place"\\
~~ мунун:мур{\tt {\small \%\{y\%\}}}н~~ N-INFL~~ ;~~ ! ``FIXME:"

@@

Also, despite the good coverage, there are still a number of grammatical forms that have not been implemented into the transducer.  For example, one such form is historically the negative of the eyewitness past tense, but is now used (mostly with a question clitic) in a certain type of modal expression;\footnote{A surprised contradictory expression, like [Идиштерди жуубадымбы ?] \eng{Did I not just wash the dishes ??}} this cannot be tagged as the negative of the eyewitness past tense, since a suppletive form is tagged that way.  Other shortcomings of the transducer are that it is not set up to deal with affixes on acronyms/abbreviations or numerals/digits (e.g., [АКШнын] \eng{The USA's}, [100гө] \eng{up to 100}) or capitalisation changes on lemmas that occur in different word classes (e.g., [Финландия] \eng{Finland}, but [финландиялык] \eng{Finnish}).

>>>>

%FIXED: this should be closer to the 200 word limit, and less like the intro pargraph

@@

\subsection{Desonorisation}
Desonorisation \citep{washington10} happens to /N/ when it follows any consonant, and to /L/ when it follows a consonant of equal or lower sonority (i.e., /л/, nasals (/м/, /н/, /ң/), and obstruents, but not /й/, /р/, or vowels).  The resulting surface consonant is [д] for both /N/ and /L/, unless it follows a voiceless consonant, in which case it surfaces as [т].  An example includes the accusative and plural suffixes, as in table~\ref{exdesonorisation}.
% FIXED: This should point to the table ?

@@

%FIXED: do something with these: make them prettier, remove them, explain them better, ....?
\begin{figure}
\caption{Example of use of epenthetic vowel \{y\}.}
~\\

 орун:ор{\tt {\small \%\{y\%\}}}н~~ N-INFL~~ ;~~ ! ``place''\\
~~ мурун:мур{\tt {\small \%\{y\%\}}}н~~ N-INFL~~ ;~~ ! ``nose''

@@

Also, despite the good coverage, there are still a number of grammatical forms that have not been implemented into the transducer.  For example, one such form is historically the negative of the eyewitness past tense, but is now used (mostly with a question clitic) in a certain type of modal expression;\footnote{The semantics are a sort of expression of surprise at others not having noticed something; e.g., [Идиштерди жуубадымбы !] \eng{Did I not just wash the dishes !?}} this cannot be tagged as the negative of the eyewitness past tense, since a suppletive form is tagged that way.  Other shortcomings of the transducer are that it is not set up to deal with affixes on acronyms/abbreviations or numerals/digits (e.g., [АКШнын] \eng{The USA's}, [100гө] \eng{up to 100}) or capitalisation changes on lemmas that occur in different word classes (e.g., [Финландия] \eng{Finland}, but [финландиялык] \eng{Finnish}).
